---
title: 'Chapter 2: Stack Overflow  Developer Survey'
author: "Isabella Benabaye"
date: "7/3/2020"
output: html_document
---
```{r imports}
library(tidyverse)
library(tidymodels)
library(hrbrthemes)
library(extrafont)
loadfonts(device = "win", quiet = TRUE) ## to load the font
theme_set(theme_ipsum(base_family = "IBM Plex Sans", base_size = 13, axis_title_size = 14))
  
```

# Import data
```{r}
stack_overflow <- read_csv("https://raw.githubusercontent.com/juliasilge/supervised-ML-case-studies-course/master/data/stack_overflow.csv")
```

# Explore the Stack Overflow survey
```{r}
glimpse(stack_overflow)

# Count for 'remote'
stack_overflow %>% 
  count(remote, sort = TRUE)

# Count for 'country'
stack_overflow %>% 
  count(country, sort = TRUE)
```

Remote: there are way more people who don't work remotely than those that do. The dataset is imbalanced.

Country: Most of the respondents are from the U.S. (~50%), then the U.K. (18%). The rest of the 32% of the respondents are from Germany, India, and Canada.

```{r}
stack_overflow %>% 
  ggplot(aes(remote, years_coded_job)) +
  geom_boxplot() +
  labs(x = NULL, y = "Years of professional coding experience")
```

Those that work remotely have more varied years of experience and a higher median, while those that don't work remotely are more centered at those who have less years of experience. Both groups have the same range though, from those who have 0 to 20 years of experience.

